\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Yariel Mercado}}\\
	yariel.mercado1@upr.edu $\cdot$ 939-263-3947 $\cdot$ https://github.com/Mercrist/ · https://www.linkedin.com/in/yariel-mercado/\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{University of Puerto Rico at Mayagüez} \hfill Expected Graduation Date: May 2024\\	
B.S. Software Engineering \textit{GPA: \bf{3.72}} 

\vspace{2mm}
\begin{tabular}{ l l }
	\textbf{Relevant Coursework:} Applied Data Structures \& Algorithms, Intro to SWE, Software Design \& Testing, \\ Machine Learning, Operating Systems, Cryptography (current), Databases (current)
\vspace{2mm}
\end{tabular}

\header{Technical Skills}
\begin{tabular}{ l l }
	Programming Languages: & Python, Java, C/C++    \\
	Software Tools: & HTML, CSS, Flask, pandas, JUnit, Guice, Mockito, TensorFlow \\
	Other Tools:   & Git, Perforce, \LaTeX{}, SQL \\
	
\end{tabular}
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{-1mm}
\textbf{UPRM} \hfill On-Site\\

\textit{OS Teaching Assistant} \hfill August 2023 - Present \\
\vspace{-2mm}
\begin{itemize} \itemsep -1pt
	\item Placed \textbf{in charge} of 30+ students for the weekly Operating Systems laboratories.
	\item \textbf{Reinforced} core concepts, in C, while writing and administering exams.
\end{itemize}
\vspace{-2mm}

\textbf{Google} \hfill On-Site\\
\textit{Google Chat Backend Intern} \hfill May 2023 - August 2023\\
\vspace{-2mm}
\begin{itemize} \itemsep -1pt
	\item \textbf{Introduced} custom metrics collected from \textbf{Spanner} RPCs.
	\item Surfaced the metrics to a live, time-series dashboard tracking over 150+ actions and utilized by \textbf{dozens} of teams within Chat.
	\item \textbf{Designed} unit \& integration tests to evaluate the metrics via internal Java frameworks.
\end{itemize}
\vspace{-2mm}

\textbf{NVIDIA} \hfill Remote\\
\textit{GPU Design Verification Intern} \hfill May 2022 - August 2022\\
\vspace{-2mm}
\begin{itemize} \itemsep -1pt
	\item \textbf{Engineered} a metrics dashboard which unified \textbf{80} hardware teams' data onto Excel.
	\item \textbf{Doubled} the efficiency of the development cycle by rewriting the script's logic. 
	\item Parsed CSV, YAML, and XLSX files, organized the data onto \textbf{pandas} dataframes, and wrote via the \textbf{XlsxWriter} library. 
\end{itemize}
\vspace{-2mm}

\textbf{Google} \hfill Remote\\
\textit{Tech Exchange Scholar} \hfill January 2022 - May 2022\\
\vspace{-2mm}
\begin{itemize} \itemsep -1pt
	\item Selected, after several interview rounds, to become a part of Google's Tech Exchange program. 
	\item Learned \textbf{industry best practices} under the supervision of Google engineers while launching two, full stack websites.
\end{itemize}
\vspace{-2mm}

\header{Technical Projects}
{\textbf{Tweets Disaster Classification}} \hfill May 2023 \\
\vspace{-2mm}
\begin{itemize} \itemsep -1pt
\item Reached the \textbf{top 10} rankings of a competition with a binary text classifier. 

\item Attained high accuracies by implementing FFNNs \& CNNs via \textbf{TensorFlow}.

\item Utilized \textbf{Matplotlib} to develop the frequency analysis for the data.
\end{itemize}
\vspace{-2mm}

{\textbf{Pathway Internships}} \hfill April 2022 \\
\vspace{-2mm}
\begin{itemize} \itemsep -1pt
\item Deployed with \textbf{Heroku} an internship review website alongside teammates at Google.

\item Allows users to post internship reviews for a company under their account. Company scores are appropriately updated and ranked.

\item Built the backend utilizing the \textbf{Flask} framework. User data is \textbf{securely encrypted} and stored along with reviews in a CRUD, \textbf{MongoDB} database. 
\end{itemize}

{\textbf{Embedded Systems Elevator Project}} \hfill \hfill July 2021-December 2021\\
\vspace{-2mm}

\begin{itemize} \itemsep -1pt
\item Developed a virtual elevator management system along members of the RUMarino embedded division.

\item \textbf{Mentored} first years collaborating with the team in: \textbf{OOP, C++, and Git}.

\item Utilizing two Arduinos serially connected to a laptop, the elevator system, written in \textbf{C++}, was controlled via a \textbf{Python} GUI on a laptop.\\
\end{itemize}
\vspace*{-0.5mm}

\header{Associations}

\vspace{-1mm} \textbf{Computer Alliance of Hispanic Serving Institutions (CAHSI)} \hfill August 2021-Present\\
\begin{itemize} \itemsep -1pt
\vspace{-2mm}
\item Assisted and mentored several sessions for CAHSI's Coding Club, focused on DS\&A. \\
\end{itemize}

\vspace{-1mm}
\textbf{RUMarino- Autonomous Water Vehicle Club} \hfill July 2021-May 2022 \\ 
\vspace{-2mm}
\begin{itemize} \itemsep -1pt
\item Formed an integral part of the software development process of the submersible. \\ 
\end{itemize}
 


\ 
\end{document}
